# DataSF

Getting data from DataSF is a matter of copying the relevant URL into one of R's many read functions, e.g. `readr::read_csv`, `jsonlite::fromJSON`, `st::st_read`, etc.

```{r}
library(readr)
library(sf)

reg_businesses <- read_csv("https://data.sfgov.org/resource/g8m3-pdis.csv")
```

::: callout-warning
Behind the scenes there is a limit parameter that defaults to 1000, *even if the 'All data' radio button is selected.* To retrieve all the data, either read the same URL with the RSocrata package:\

```{r eval = FALSE}
reg_businesses <- RSocrata::read.socrata("https://data.sfgov.org/resource/g8m3-pdis.csv")
```

Or append `?$limit=9999999` to the end of the URL:

```{r eval = FALSE}
reg_businesses <- read_csv("https://data.sfgov.org/resource/g8m3-pdis.csv?$limit=9999999")
```
:::

Read in a 'spatial' object with `st_read` and the URL with the geojson file extension:

```{r}
sup_dists <- st_read("https://data.sfgov.org/api/geospatial/f2zs-jevy?accessType=DOWNLOAD&method=export&format=GeoJSON")
```
