# Excel Stuff

[{readxl}](https://readxl.tidyverse.org/) is the best package to *read* excel (xlsx) files.

```{r eval = FALSE}
library(readxl)
df <- read_xlsx("path_to_xlsx")
```


[{writexl}](https://docs.ropensci.org/writexl/) is the best package to *write* excel (xlsx) files.

```{r eval = FALSE}
library(writexl)
write_xlsx(mtcars, "car_data.xlsx")
```

You can also pass a named list of data frames to `write_xlsx`, and it will write each data frame to a separate sheet in the workbook.

```{r eval = FALSE}
l <- list(
  "Car data" = mtcars,
  "Flower data" = iris
)

write_xlsx(l, "my_data.xlsx")
```

With the `{purrr}` and [`{kapow}` packages](https://github.com/daranzolin/kapow) package you can loop through each sheet in a workbook and assign the table to its sheet name in your global environment:

```{r eval = FALSE}
library(readxl)
library(purrr)
library(kapow) # remotes::install_github("daranzolin/kapow)

xlsx_path <- "path_to_xlsx"
sheet_names <- excel_sheets(xlsx_path)
sheet_names %>% 
  map(\(sheet) read_excel(xlsx_path, sheet = sheet)) %>% 
  set_names(sheet_names) %>% 
  kapow()
```

To apply special formatting to an Excel workbook in R you can use the [{openxlsx} package.](https://github.com/ycphs/openxlsx) Here's an example of how OEWD writes to xlsx:

```{r eval = FALSE}
library(openxlsx)
write_oewd_xlsx <- function(data, sheet_name, file, dateFormat = "yyyy/mm/dd", overwrite = FALSE) {
  wb <- createWorkbook()
  addWorksheet(wb, sheet_name)
  style <- createStyle(halign = "LEFT", valign = "CENTER")
  setColWidths(wb, sheet = 1, cols = 1:ncol(data), widths = "auto")
  addStyle(wb, 1,
           cols = 1:(ncol(data) + 1),
           rows = 1:(nrow(data) + 1),
           style = style,
           gridExpand = TRUE)
  headerStyle <- createStyle(
    halign = "LEFT",
    textDecoration = "Bold"
  )
  writeData(wb, 1, data, headerStyle = headerStyle)
  options("openxlsx.dateFormat" = dateFormat)
  saveWorkbook(wb, file, overwrite = overwrite)
}

write_oewd_xlsx(mtcars, "Car data", "car_data.xlsx")
```

